---
title: "Drivers of methane flux dynamics in a freshwater reservoir with variable dissolved oxygen "

author: "Bibek Kandel"
date: "`r Sys.Date()`"
output: html_document
---


```{r, include=FALSE}

#Load libraries
pacman::p_load(knitr, DiagrammeRsvg, rsvg, mvnormalTest, lavaan, lavaanPlot, dplyr, readr, tidyr, lubridate, ggcorrplot, purrr, broom, leaps, piecewiseSEM, gridExtra, htmltools, zoo, tidyverse)


```


```{r}
#This chunk of code will load up the dataset with methane flux and associated driver variables from comp_data.csv created using script_to_create_comp_dataset.R

#This will pull the methane flux daily data which only pass minimum half hourly test of >=20
comp_data <- read_csv("https://raw.github.com/bee-bake/5_yrs_FCR_flux_analysis/main/comp_data.csv", show_col_types = FALSE) |> 
  mutate(Date = date)

```



```{r}
#Import ghg from EDI and Filter the date and depth needed and convert to fluxes
#Do you get a different answer if you just extract the date part of the time rather than rounding?

ghg_FCR <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/551/9/98f19e7acae8bea7d127c463b1bb5fbc") |>  
  mutate(DateTime = as_datetime(DateTime, tz="EST"), 
         DateTime = date(DateTime)) |>  
  filter(Reservoir == "FCR", Site == 50, DateTime >= "2020-01-01")

#Extract the volume of the depth of our interest from EDI to estimate volume-weighted methane in the following chunks
#Get bathymetry data from EDI
ghg_FCR_EDI <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/1254/1/f7fa2a06e1229ee75ea39eb586577184")

summarized_volumes <- tibble(
  Depth_m = c(0.1, 1.6, 3.8, 5, 6.2, 8, 9),
  Volume_L = c(34590292.2, 22032551, 8265212, 4772921, 2697184, 515240, 9358))

#Note: For 0.1m volume, first the average of 0m and 0.4m was taken which gives us the volume at 0.2m and then again average between volumes at 0m and 0.2m will give us that at 0.1m.

```



```{r}
#PREPARING DISSOLVED GHG DATASET
#Calculate mean methane from two replicates and filter data from April-November
## Pivot wider
ghg_conc <- ghg_FCR |>   
  select(DateTime,Rep,CH4_umolL,CO2_umolL, Depth_m) |>  
  summarize(mean_CH4 = mean(CH4_umolL, na.rm = TRUE),
            mean_CO2 = mean(CO2_umolL, na.rm = TRUE),
            .by = c("DateTime", "Depth_m"))


#only summer (April - November)
ghg_conc_summer <- ghg_conc |> 
  filter(DateTime >= "2020-04-01 00:00:00" & DateTime < "2024-11-30 00:00:00") |> 
  select(DateTime, Depth_m, mean_CH4)

```


```{r}
####This chunk will estimate the volume-weighted methane by multiplying the mean CH4 concentrations at each depth of interest and the respective volume of each depth in units of mol (umol/1000000)
#dissolved methane 
sub_ghg_conc <- ghg_conc_summer |> 
  mutate(Date = date(DateTime)) |> 
  select(Date, mean_CH4, Depth_m)


#merge the summarized volumes with dissolved methane data
Vol_Weighted_CH4 <- left_join(sub_ghg_conc, summarized_volumes, by = "Depth_m") 


#Calculate volume-weighted dissolved methane concentration. Can you put units on this?
Vol_Weighted_CH4 <- Vol_Weighted_CH4 |> 
  mutate(VW_methane = (mean_CH4*Volume_L)/1000000)

#Pivot wider and join with comprehensive dataset
selected_CH4 <- Vol_Weighted_CH4 |> 
  select(Date, Depth_m, VW_methane) |> 
  filter(Depth_m != 6.0)|> #take out the 2 measurements at 6m in the data frame
  pivot_wider(names_from = Depth_m, values_from = VW_methane, values_fill = NA) |> 
  rename(CH4_surface = "0.1",
         CH4_1.6m = "1.6",
         CH4_3.8m = "3.8",
         CH4_5m = "5",
         CH4_6.2m = "6.2",
         CH4_8m = "8",
         CH4_9m = "9") 


#join with comp_data
full_Data <- left_join(comp_data, selected_CH4, by = "Date")

```


```{r}
#Select the columns needed
ready_data <- full_Data |> 
  select(Date, daily_CH4, DOsat_5m, DOsat_9m, sch_stab, 
         WindSpeed_Average_m_s, CH4_1.6m, 
         CH4_5m, CH4_9m, temp_9m, temp_5m, DOsat_surface, temp_1.6m, 
         mean_Chla, mean_fDOM) 

#rename some variables for simplicity
epi_hyp_data <- ready_data |> 
  rename(DOsat_1.6m = "DOsat_surface",
         Wind = "WindSpeed_Average_m_s")


```


We interpolate dissolved methane data at each depths separately in the following chunk.

```{r}
# #interpolation
# #reorder

# USE arrange and desc
Vol_Weighted_CH4_ordered <- Vol_Weighted_CH4 |> 
  arrange(Date, Depth_m)

# #dissolved methane
sub_ghg_fluxes <- Vol_Weighted_CH4_ordered |> 
  select(Date, VW_methane, Depth_m)

# # Generate a sequence of daily dates
days <- seq(min(sub_ghg_fluxes$Date), max(sub_ghg_fluxes$Date), by = "day")
layers <- c(0.1,1.6,3.8,5,6.2,8,9)
data <- expand.grid(Date = days, Depth_m = layers)  # Create a full grid
#
# #merge
CH4_int <- left_join(data, sub_ghg_fluxes, by=c("Date","Depth_m"))
#
GHG_int_final <- CH4_int |> 
  group_by(Depth_m) |>   # Process each layer separately
  mutate(CH4_int = na.approx(VW_methane, Date, rule = 2)) %>%  # Linear interpolation
  ungroup() %>%
  select(-VW_methane)

#Pivot wider and join with EddyFlux data
selected_CH4_int <- GHG_int_final |> 
  select(Date, Depth_m, CH4_int) |> 
  pivot_wider(names_from = "Depth_m", values_from = "CH4_int") |> 
  rename(iCH4_surface = "0.1",
         iCH4_1.6m = "1.6",
         iCH4_3.8m = "3.8",
         iCH4_5m = "5",
         iCH4_6.2m = "6.2",
         iCH4_8m = "8",
         iCH4_9m = "9") |> 
  select(-iCH4_surface, -iCH4_3.8m, -iCH4_6.2m, -iCH4_8m)

#join with full_data
epi_hyp_int <- left_join(epi_hyp_data, selected_CH4_int, by = "Date")

```


Let's plot the discrete dissolved methane concentrations before and after interpolation to check they align with each other. 


```{r}
#ADD PLOT OF epi_hyp_int to confirm that it looks like you expect it to look
gut_check <- epi_hyp_int |> 
  select(Date, daily_CH4, CH4_1.6m, CH4_5m, CH4_9m,
         iCH4_1.6m, iCH4_5m, iCH4_9m)

# Select column pairs for comparison
selected_pairs <- list(
  c("CH4_1.6m", "iCH4_1.6m"),
  c("CH4_5m", "iCH4_5m"),
  c("CH4_9m", "iCH4_9m"),
  c("daily_CH4", "daily_CH4")
)

# Define colors for the two variables in each pair
colors <- c("blue", "red")

# Define a smaller legend size
legend_size <- 0.6

# Create a 2x3 plotting layout
par(mfrow = c(2, 3))  

# Loop through each selected pair and plot them
for (i in 1:length(selected_pairs)) {
  vars <- selected_pairs[[i]]
  
  # Plot first variable
  plot(gut_check$Date, gut_check[[vars[1]]], type = "p", col = colors[1], lwd = 2,
       xlab = "", ylab = "Value", main = paste("Pair", i, ":", vars[1], "vs", vars[2]))
  
  # Add second variable using lines()
  lines(gut_check$Date, gut_check[[vars[2]]], col = colors[2], lwd = 2)
  
  # Add a legend
  legend("topright", legend = vars, col = colors, pch = 1, lty = 1, lwd = 2, cex = legend_size, bg=rgb(1, 1, 1, 0.5))
}


```


#########################################################

### Structural Equation Modeling

#Resources:

#https://bookdown.org/luguben/EFA_in_R/determining-the-number-of-factors-1.html

#https://cran.r-project.org/web/packages/lavaanPlot/vignettes/Intro_to_lavaanPlot.html

#https://people.ucsc.edu/~zurbrigg/psy214b/09SEM8a.pdf

#Hu, L. T., & Bentler, P. M. (1999). Cutoff criteria for fit indexes in covariance structure analysis: Conventional criteria versus new alternatives. Structural equation modeling: a multidisciplinary journal, 6(1), 1-55.

#Sathyanarayana, S., & Mohanasundaram, T. (2024). Fit indices in structural equation modeling and confirmatory factor analysis: reporting guidelines. Asian Journal of Economics, Business and Accounting, 24(7), 561-577.


- First, we explored the relationships among various water quality variables and methane fluxes using a correlation plot. We did not include the independent variables strongly correlated with each other in the models to remove the effects of multicollinearity.


```{r}
#correlations
cor_data <- epi_hyp_int |> 
  select(-Date)

cor_matrix <- cor(cor_data, use="pairwise.complete.obs")
ggcorrplot(cor_matrix,
           lab = TRUE, lab_size = 2, tl.cex = 8)

```


The correlogram showed that the daily methane flux was most negatively correlated with dissolved oxygen saturation at 5m depth and 9m depth among the variables used. Also, daily methane flux was most positively correlated with volume-weighted dissolved methane concentration at 5m, thermocline depth and blue-green algae concentrations. #We then used short-listed variables from correlation analysis to define path analysis models and tested them against the weekly data. 

The model assumptions about univariate and multivariate normality was tested using shapiro-Wilk test and Mardia multivariate normality test.



```{r}
#Assessing assumptions about the distribution of measured variables
#Select only the columns we want to model
corr_data <- epi_hyp_int |> 
  select(daily_CH4, DOsat_5m, DOsat_9m, 
         sch_stab, Wind, iCH4_1.6m, 
         iCH4_5m, iCH4_9m, temp_9m, temp_5m, 
         DOsat_1.6m, temp_1.6m, mean_Chla, mean_fDOM,
         DOsat_1.6m)

#Test multivariate normality
mvnout <- mardia(corr_data)
mvnout$uv.shapiro #extract shapiro-Wilk univariate normality test statistics
mvnout$mv.test #Mardia multivariate normality test

```


- Results from both the univariate and multivariate tests indicate that the most measures do not come from multivariate normal distributions. Thus, we'll use MLM as an estimator in the later SEM analysis.

#Reference: https://www.regorz-statistik.de/blog/lavaan_normality.html


```{r}
#NORMALIZE THE DATASET
data_scaled <- scale(corr_data)

```


### Individual path models and drivers selection

The piecewise SEM produces no valid global covariance matrix unlike latent variable based SEM, alternative goodness-of-fit tests are necessary. The typical approach uses Shipley's test of directed separation. This procedure tests the assumption that all variables are conditionally independent. In simplest terms, conditional independence implies that there are no missing relationships among unconnected variables (Shipley 2000a).

To compare standardized regression coefficients, we re-fit the model in lavaan package and assess the model fit using standardized test statistics (the ratio of chi-squared value to the degrees of freedom greater than 3), root mean squared error approximation (RMSEA) and standard root mean residual (SRMR) less than 0.1 and comparative fit index (CFI) grater than 0.9. 


The regression coefficients represent the strength of the relationship between latent constructs/ independent variables and dependent variable(s). Since, the latent constructs are correlated, the regression coefficients are partial coefficients, interpreted as the amount of change in dependent/ exogenous variable given a unit change in independent/ latent variable, controlling for the effects of other variables in the model.



```{r}
#select variables of interest and include lags informed from cross-correlation plots
data_flux <- epi_hyp_int |> 
  select(DOsat_9m, temp_1.6m, temp_9m, temp_5m,
         iCH4_5m, iCH4_1.6m, DOsat_5m,
         sch_stab, DOsat_1.6m, daily_CH4, 
         Wind, iCH4_9m, mean_Chla, mean_fDOM) |>
  mutate(temp_1.6m_lag3 = lag(temp_1.6m, 3),
         mean_fDOM_lag1 = lag(mean_fDOM, 1)) |> 
  na.omit()

#This is same dataset data_flux but with Date for later use
data_flux_w_date <- epi_hyp_int |> 
  select(Date, DOsat_9m, temp_1.6m, temp_9m, temp_5m,
         iCH4_5m, iCH4_1.6m, DOsat_5m,
         sch_stab, DOsat_1.6m, daily_CH4, 
         Wind, iCH4_9m, mean_Chla, mean_fDOM) |>
  mutate(temp_1.6m_lag3 = lag(temp_1.6m, 3),
         mean_fDOM_lag1 = lag(mean_fDOM, 1)) |> 
  na.omit()

```


```{r}
#Check lags using cross-correlation function
#Note: this is just for temp_1.6m and daily_CH4 but did the same for all variables of interest. A cross-correlation plot helps to understand how two time series are related over time, especially when the effect of one variable may be delayed or lagged relative to the other. A cross-correlation function (CCF) plot shows how strongly two time series are correlated as you shift one of them forward or backward in time.

ccf(data_flux$temp_1.6m, data_flux$daily_CH4, lag.max = 5)


```


Diffusion model: In this concept, CH4 diffusion/ebullition from hypolimnion to the epilimnion and subsequent flux to the atmosphere was modeled. 

```{r}
#diffusion/ebullition pathways model
#fit the path models
model_flux <- psem(
  lm(daily_CH4 ~ Wind + iCH4_5m + iCH4_1.6m + iCH4_9m, data_flux),
  lm(iCH4_5m ~ iCH4_9m, data_flux)

)

summary(model_flux)


####MODEL TESTING IN LAVAAN PACKAGE######
#scale the dataset
data_flux_scaled <- scale(data_flux)

model_flux <- '

  daily_CH4 ~ Wind + iCH4_5m + iCH4_1.6m + iCH4_9m
  iCH4_5m ~ iCH4_9m


'


fit.mod <- sem(model_flux, data = data_flux_scaled, std.lv = TRUE, estimator = "MLM")
#MODEL FIT (Ideally non-significant p-value OR the ratio of chisq.scaled:df.scaled less than 5)
fitMeasures(fit.mod, c("chisq.scaled", "df.scaled", "pvalue.scaled"))
#Check RMSEA to estimate the discrepancy between the model-based and observed correlation matrices which takes into account both chi-squared value and model parsimony.
#We want RMSEA <= 0.1
fitMeasures(fit.mod, c("rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "rmsea.pvalue.scaled"))
#Check CFI and SRMR
#We want CFI >= 0.9 and SRMR <= 0.08
fitMeasures(fit.mod, c("cfi.scaled", "srmr"))

#visualize the path diagrams
lavaanPlot(model = fit.mod, , graph_options = list(rankdir = "BT"), node_options=list(shape="box", fontname="Helvetica"), edge_options=list(color="grey"), coefs = TRUE, stand = TRUE, stars = c("regress", "latent"), digits=3, sig = TRUE)


```


Diffusion/ebullition ALTERNATIVE model: This is a slightly modified version of above model where we add a new data point (diffusion pathway from 5m to 1.6m), which destroys the model. This is why we did not include this pathway in the basic diffusion/ebullition model.

```{r}
#diffusion/ebullition pathways ALTERNATIVE model
#fit the path models
model_flux <- psem(
  lm(daily_CH4 ~ Wind + iCH4_5m + iCH4_1.6m + iCH4_9m, data_flux),
  lm(iCH4_1.6m ~ iCH4_5m, data_flux),
  lm(iCH4_5m ~ iCH4_9m, data_flux)

)

summary(model_flux)


####MODEL TESTING IN LAVAAN PACKAGE######
#scale the dataset
data_flux_scaled <- scale(data_flux)

model_flux <- '

  daily_CH4 ~ Wind + iCH4_5m + iCH4_1.6m + iCH4_9m
  iCH4_1.6m ~ iCH4_5m
  iCH4_5m ~ iCH4_9m


'


fit.mod <- sem(model_flux, data = data_flux_scaled, std.lv = TRUE, estimator = "MLM")
#MODEL FIT (Ideally non-significant p-value OR the ratio of chisq.scaled:df.scaled less than 5)
fitMeasures(fit.mod, c("chisq.scaled", "df.scaled", "pvalue.scaled"))
#Check RMSEA to estimate the discrepancy between the model-based and observed correlation matrices which takes into account both chi-squared value and model parsimony.
#We want RMSEA <= 0.1
fitMeasures(fit.mod, c("rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "rmsea.pvalue.scaled"))
#Check CFI and SRMR
#We want CFI >= 0.9 and SRMR <= 0.08
fitMeasures(fit.mod, c("cfi.scaled", "srmr"))

#visualize the path diagrams
lavaanPlot(model = fit.mod, , graph_options = list(rankdir = "BT"), node_options=list(shape="box", fontname="Helvetica"), edge_options=list(color="grey"), coefs = TRUE, stand = TRUE, stars = c("regress", "latent"), digits=3, sig = TRUE)


```




Diffusion/Ebullition with physical drivers model: In this concept, physical drivers were added to the diffusion/ebullition model.


```{r}
#Diffusion/Ebullition with physical drivers
#fit the path models
model_flux <- psem(
  lm(daily_CH4 ~ Wind + iCH4_5m + temp_1.6m_lag3 + iCH4_1.6m + iCH4_9m + sch_stab, data_flux),
  lm(iCH4_5m ~ DOsat_5m + temp_5m + iCH4_9m + sch_stab, data_flux)

)

summary(model_flux)


####MODEL TESTING IN LAVAAN PACKAGE######
#scale the dataset
data_flux_scaled <- scale(data_flux)

model_flux <- '

  daily_CH4 ~ Wind + iCH4_5m + temp_1.6m_lag3 + iCH4_1.6m + iCH4_9m + sch_stab
  iCH4_5m ~ DOsat_5m + temp_5m + iCH4_9m + sch_stab


'


fit.mod <- sem(model_flux, data = data_flux_scaled, std.lv = TRUE, estimator = "MLM")
#MODEL FIT (Ideally non-significant p-value OR the ratio of chisq.scaled:df.scaled less than 5)
fitMeasures(fit.mod, c("chisq.scaled", "df.scaled", "pvalue.scaled"))
#Check RMSEA to estimate the discrepancy between the model-based and observed correlation matrices which takes into account both chi-squared value and model parsimony.
#We want RMSEA <= 0.1
fitMeasures(fit.mod, c("rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "rmsea.pvalue.scaled"))
#Check CFI and SRMR
#We want CFI >= 0.9 and SRMR <= 0.08
fitMeasures(fit.mod, c("cfi.scaled", "srmr"))

#visualize the path diagrams
lavaanPlot(model = fit.mod, , graph_options = list(rankdir = "BT"), node_options=list(shape="box", fontname="Helvetica"), edge_options=list(color="grey"), coefs = TRUE, stand = TRUE, stars = c("regress", "latent"), digits=3, sig = TRUE)


```


Diffusion/Ebullition with physical and biological drivers model: In this concept, physical and biological drivers were added to the diffusion/ebullition model.


```{r}
#Diffusion/Ebullition with physical and Biological drivers
#fit the path models
model_flux <- psem(
  lm(daily_CH4 ~ Wind + iCH4_5m + temp_1.6m_lag3 + iCH4_1.6m + iCH4_9m + sch_stab + mean_Chla, data_flux),
  lm(iCH4_5m ~ DOsat_5m + temp_5m + mean_fDOM + iCH4_9m + sch_stab, data_flux)

)

summary(model_flux)


####MODEL TESTING IN LAVAAN PACKAGE######
#scale the dataset
data_flux_scaled <- scale(data_flux)

model_flux <- '

  daily_CH4 ~ Wind + iCH4_5m + temp_1.6m_lag3 + iCH4_1.6m + iCH4_9m + sch_stab + mean_Chla
  iCH4_5m ~ DOsat_5m + temp_5m + mean_fDOM + iCH4_9m + sch_stab


'


fit.mod <- sem(model_flux, data = data_flux_scaled, std.lv = TRUE, estimator = "MLM")
#MODEL FIT (Ideally non-significant p-value OR the ratio of chisq.scaled:df.scaled less than 5)
fitMeasures(fit.mod, c("chisq.scaled", "df.scaled", "pvalue.scaled"))
#Check RMSEA to estimate the discrepancy between the model-based and observed correlation matrices which takes into account both chi-squared value and model parsimony.
#We want RMSEA <= 0.1
fitMeasures(fit.mod, c("rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "rmsea.pvalue.scaled"))
#Check CFI and SRMR
#We want CFI >= 0.9 and SRMR <= 0.08
fitMeasures(fit.mod, c("cfi.scaled", "srmr"))

#visualize the path diagrams
lavaanPlot(model = fit.mod, , graph_options = list(rankdir = "BT"), node_options=list(shape="box", fontname="Helvetica"), edge_options=list(color="grey"), coefs = TRUE, stand = TRUE, stars = c("regress", "latent"), digits=3, sig = TRUE)

```


```{r}
#Statistical test
## Compare early summer (Apr-July) and late summer (Aug - Nov) fluxes

seasonal_flux <- data_flux_w_date |> 
  select(Date,daily_CH4) |> 
  mutate(Year = year(Date), 
         Month = month(Date)) |> 
  mutate(Season = ifelse(Month == 4 | Month == 5 | Month == 6 | Month == 7, "Early","Late"))

#Difference in fluxes among years 
seasonal_diff <- seasonal_flux |> 
  ungroup() |>
  select(Year, daily_CH4) |> 
  group_by(Year) |> 
  summarise_all(median,na.rm=TRUE)


# Pairwise Wilcoxon test among years
pairwise.wilcox.test(seasonal_flux$daily_CH4, seasonal_flux$Year, p.adjust.method = "BH")


#Mean by seasons and years
seasonal_agg <- seasonal_flux |> 
  ungroup() |> 
  group_by(Year, Season) |>  
  dplyr::summarise(CH4_mean = mean(daily_CH4, na.rm = TRUE),
                   CH4_sd = sd(daily_CH4, na.rm = TRUE))


#Test for seasonal difference overall
wilcox.test(daily_CH4 ~ Season, data = seasonal_flux)

#Seasonal difference within each year
seasonal_flux %>%
  group_by(Year) %>%
  summarise(p_value = wilcox.test(daily_CH4 ~ Season)$p.value)


#plots
# Yearly comparison
ggplot(seasonal_flux, aes(x = factor(Year), y = daily_CH4)) +
  geom_boxplot() +
  labs(x = "Year", y = "CH4 Flux", title = "CH4 Flux by Year")

# Seasonal comparison
ggplot(seasonal_flux, aes(x = Season, y = daily_CH4)) +
  geom_boxplot() +
  labs(x = "Season", y = "CH4 Flux", title = "Early vs Late Season CH4 Flux")



```

```{r}
#Interaction effect of DO and temp on fluxes
seasonal_flux <- data_flux_w_date |>
  select(Date, daily_CH4, DOsat_5m, temp_5m)

#Linear model between flux and temperature/DOsat_5m
m3 <- lm(daily_CH4 ~ DOsat_5m + temp_5m + DOsat_5m*temp_5m , seasonal_flux)
summary(m3)

```


```{r}
# Add a description of what you are doing here and why
# Add Year, Month, Season, and DO class
seasonal_flux <- data_flux_w_date |>
  select(Date, daily_CH4, DOsat_9m) |>
  mutate(
    Year = year(Date),
    Month = month(Date),
    Season = ifelse(Month %in% 4:7, "Early", "Late"),
    DO_Class = ifelse(DOsat_9m < 20, "Low_DO", "High_DO")
  )

# Summary median CH4 flux by Year, DO_Class, and Season
flux_summary <- seasonal_flux |>
  group_by(Year, Season, DO_Class) |>
  summarise(median_flux = median(daily_CH4, na.rm = TRUE), .groups = "drop")

# Wilcoxon test comparing years within each DO class
# Pairwise comparison of years for Low_DO only
low_DO_data <- filter(seasonal_flux, DO_Class == "Low_DO")
pairwise_low <- pairwise.wilcox.test(low_DO_data$daily_CH4, low_DO_data$Year, p.adjust.method = "BH")

# Pairwise comparison of years for High_DO only
high_DO_data <- filter(seasonal_flux, DO_Class == "High_DO")
pairwise_high <- pairwise.wilcox.test(high_DO_data$daily_CH4, high_DO_data$Year, p.adjust.method = "BH")

# Seasonal test within DO groups
pairwise_season_low <- pairwise.wilcox.test(low_DO_data$daily_CH4, low_DO_data$Season, p.adjust.method = "BH")
pairwise_season_high <- pairwise.wilcox.test(high_DO_data$daily_CH4, high_DO_data$Season, p.adjust.method = "BH")


m2 <- lm(daily_CH4 ~ Season + DO_Class + Season*DO_Class, seasonal_flux)
summary(m2)

# Yearly comparison
ggplot(seasonal_flux, aes(x = factor(Year), y = DOsat_9m)) +
  geom_boxplot() +
  geom_point() +
  labs(x = "Year", y = "DOsat_9m", title = "DOsat by Year")

```

```{r}
#select variables 
seasonal_flux <- data_flux_w_date |>
  select(Date, DOsat_5m, DOsat_9m) |> 
  mutate(Year = year(Date))

# Convert to long format
seasonal_flux_long <- seasonal_flux |> 
  pivot_longer(cols = c(DOsat_5m, DOsat_9m), 
               names_to = "Depth", 
               values_to = "DOsat")

# Faceted panel plot
ggplot(seasonal_flux_long, aes(x = factor(Year), y = DOsat)) +
  geom_boxplot(fill = "skyblue") +
  geom_jitter(width = 0.2, alpha = 0.3, color = "black") +
  facet_wrap(~ Depth, nrow = 1, scales = "free_y") +
  labs(x = "Year", y = "DO Saturation", title = "Yearly DO Saturation at 5m and 9m") +
  theme_bw() +
  theme(strip.text = element_text(size = 12, face = "bold"))

# Pairwise Wilcoxon test among years
pairwise.wilcox.test(seasonal_flux$DOsat_5m, seasonal_flux$Year, p.adjust.method = "BH")

# Can you denote which years the oxygenation system was on. Maybe different fill colors in the box?
# Are you go to denote significance in the plots? 





```


