---
title: "Drivers of methane flux dynamics in a freshwater reservoir with variable dissolved oxygen "

author: "Bibek Kandel"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#Load libraries
pacman::p_load(DiagrammeRsvg, rsvg, mvnormalTest, lavaan, lavaanPlot, dplyr, readr, tidyr, lubridate, ggcorrplot, purrr, broom, leaps, piecewiseSEM, gridExtra, htmltools, zoo, tidyverse)

```


```{r}
#Load up the data with methane flux (comp_data.csv created using script_to_create_comp_dataset.R) and associated driver variables
#This will pull the methane flux daily data which only pass minimum half hourly test of >=20
comp_data <- read_csv("https://raw.github.com/bee-bake/EddyFlux_data/main/comp_data.csv", show_col_types = FALSE) |> 
  select(-...1) |>   # Removes the unnecessary first column 
  rename(Date = "date")
```



```{r}
#Import ghg from EDI and Filter the date and depth needed and convert to fluxes
#Do you get a different answer if you just extract the date part of the time rather than rounding?

ghg_FCR <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/551/9/98f19e7acae8bea7d127c463b1bb5fbc") |>  
  mutate(DateTime = as_datetime(DateTime, tz="EST"), 
         DateTime = date(DateTime)) |>  
  filter(Reservoir == "FCR", Site == 50, DateTime >= "2020-01-01")

#create a hypsometric table with depth and volume (Hounshell et al. 2022)
summarized_volumes <- tibble(
  Depth_m = c(0.1, 1.6, 3.8, 5, 6.2, 8, 9),
  Volume_L = c(125594861, 101405139, 59900000, 40200000, 13900000, 14100000, 1950000)) #adapted from SI (Hounshell et al. 2020) & bathy_FCR

```



```{r}
#PREPARING DISSOLVED GHG DATASET
#Calculate mean methane from two replicates and filter data from April-November
## Pivot wider
ghg_conc <- ghg_FCR |>   
  select(DateTime,Rep,CH4_umolL,CO2_umolL, Depth_m) |>  
  summarize(mean_CH4 = mean(CH4_umolL, na.rm = TRUE),
            mean_CO2 = mean(CO2_umolL, na.rm = TRUE),
            .by = c("DateTime", "Depth_m"))


#only summer (April - November)
ghg_conc_summer <- ghg_conc |> 
  filter(DateTime >= "2020-04-01 00:00:00" & DateTime < "2024-11-30 00:00:00") |> 
  select(DateTime, Depth_m, mean_CH4)

```


```{r}
####ESTIMATE VOLUME WEIGHTED METHANE
#dissolved methane 
sub_ghg_conc <- ghg_conc_summer |> 
  mutate(Date = date(DateTime)) |> 
  select(Date, mean_CH4, Depth_m)


#merge the summarized volumes with dissolved methane data
Vol_Weighted_CH4 <- left_join(sub_ghg_conc, summarized_volumes, by = "Depth_m") 


#Calculate volume-weighted dissolved methane conc
Vol_Weighted_CH4 <- Vol_Weighted_CH4 |> 
  mutate(VW_methane = (mean_CH4*Volume_L)/1000000)

#Pivot wider and join with EddyFlux data
selected_CH4 <- Vol_Weighted_CH4 |> 
  select(Date, Depth_m, VW_methane) |> 
  pivot_wider(names_from = Depth_m, values_from = VW_methane, values_fill = NA) |> 
  rename(CH4_surface = "0.1",
         CH4_1.6m = "1.6",
         CH4_3.8m = "3.8",
         CH4_5m = "5",
         CH4_6.2m = "6.2",
         CH4_8m = "8",
         CH4_9m = "9")


#join with comp_data
full_Data <- left_join(comp_data, selected_CH4, by = "Date")

```


Let's also load in DO saturated from CTD data. Here, we aggregate DO at continuous depth data into DO at discrete depths of our interest by averaging the saturated DO across +/- 0.2m.


```{r}
#Load the dataset
#Load in CTD for surface measurements
CTD_all <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/200/15/9d741c9cced69cfd609c473ada2812b1")

```


```{r}
#DATA WITHOUT INTERPOLATION
#Considering 0.1m DO as a mean of DO around +/-0.2 m
#Calculate discrete DO at each depth of interest
CTD_profile <- CTD_all |> 
  filter(Reservoir == "FCR" & Site == 50 & 
         DateTime >= "2020-04-01 00:00:00" & DateTime < "2024-11-30 00:00:00") |>
  mutate(Date = date(DateTime),
         Month = month(Date)) |> 
  filter(Month >= 4 & Month <= 11) |> 
  select(Date, DOsat_percent, Depth_m) |> 
  filter(Depth_m >= 0 & Depth_m <= 0.3 |
           Depth_m >= 1.4 & Depth_m <= 1.8 |
           Depth_m >= 3.6 & Depth_m <= 4.0 |
           Depth_m >= 4.8 & Depth_m <= 5.2 |
           Depth_m >= 6.0 & Depth_m <= 6.4 |
           Depth_m >= 7.8 & Depth_m <= 8.2 |
           Depth_m >= 8.8 & Depth_m <= 9.2) |> 
  na.omit()

#Rounding of +/- 0.2m depths to the depths we need

CTD_profile <- CTD_profile |> 
  mutate(Depth_bin_m  = case_when(Depth_m >= 0.0 & Depth_m <= 0.3 ~ 0.1,
                                  Depth_m >= 1.4 & Depth_m <= 1.8 ~ 1.6,
                                  Depth_m >= 3.6 & Depth_m <= 4.0 ~ 3.8,
                                  Depth_m >= 4.8 & Depth_m <= 5.2 ~ 5.0,
                                  Depth_m >= 6.0 & Depth_m <= 6.4 ~ 6.2,
                                  Depth_m >= 7.8 & Depth_m <= 8.2 ~ 8.0,
                                  Depth_m >= 8.8 & Depth_m <= 9.2 ~ 9.0
                                  ))

#create a file containing datetime, depth and dissolved oxygen
DO_sat <- CTD_profile |> 
  select(Date, Depth_bin_m, DOsat_percent) |> 
  summarise(mean_DOsat = mean(DOsat_percent), .by = c("Date", "Depth_bin_m")) |> 
  rename(Depth_m = Depth_bin_m)


```


```{r}
#Select the columns needed
ready_data <- full_Data |> 
  select(Date, daily_CH4, temp_surface, DOsat_5m, DOsat_9m, sch_stab, 
         WindSpeed_Average_m_s, CH4_3.8m, thermo.depth, CH4_1.6m, CH4_surface, 
         CH4_5m, CH4_9m, temp_9m, temp_5m, temp_4m, DOsat_surface, temp_1.6m, 
         mean_Chla, mean_fDOM)


#Join CTD DOsat and stepwise datasets
#Filter only 0.1 depths 
DO_sat_surface <- DO_sat |> 
  filter(Depth_m == 0.1 | Depth_m == 3.8) |> 
  pivot_wider(names_from = Depth_m, values_from = mean_DOsat) |>
  rename(DOsat_0.1m= "0.1",
         DOsat_3.8m = "3.8")

#Merge DO and ready_data
epi_hyp_data <- left_join(ready_data, DO_sat_surface, by = "Date") |> 
  rename(DOsat_1.6m = "DOsat_surface",
         Wind = "WindSpeed_Average_m_s")

```


We interpolate dissolved methane data at each depths separately in the following chunk.

```{r}
# #interpolation
# #reorder

# USE arrange and desc
Vol_Weighted_CH4_ordered <- Vol_Weighted_CH4 |> 
  arrange(Date, Depth_m)

# #dissolved methane
sub_ghg_fluxes <- Vol_Weighted_CH4_ordered |> 
  select(Date, VW_methane, Depth_m)

# # Generate a sequence of daily dates
days <- seq(min(sub_ghg_fluxes$Date), max(sub_ghg_fluxes$Date), by = "day")
layers <- c(0.1,1.6,3.8,5,6.2,8,9)
data <- expand.grid(Date = days, Depth_m = layers)  # Create a full grid
#
# #merge
CH4_int <- left_join(data, sub_ghg_fluxes, by=c("Date","Depth_m"))
#
GHG_int_final <- CH4_int |> 
  group_by(Depth_m) |>   # Process each layer separately
  mutate(CH4_int = na.approx(VW_methane, Date, rule = 2)) %>%  # Linear interpolation
  ungroup() %>%
  select(-VW_methane)

#Pivot wider and join with EddyFlux data
selected_CH4_int <- GHG_int_final |> 
  select(Date, Depth_m, CH4_int) |> 
  pivot_wider(names_from = "Depth_m", values_from = "CH4_int") |> 
  rename(iCH4_surface = "0.1",
         iCH4_1.6m = "1.6",
         iCH4_3.8m = "3.8",
         iCH4_5m = "5",
         iCH4_6.2m = "6.2",
         iCH4_8m = "8",
         iCH4_9m = "9")

#join with full_data
epi_hyp_int <- left_join(epi_hyp_data, selected_CH4_int, by = "Date")

```


Let's plot the discrete dissolved methane concentrations before and after interpolation to check they align with each other. 


```{r}
#ADD PLOT OF epi_hyp_int to confirm that it looks like you expect it to look
gut_check <- epi_hyp_int |> 
  select(Date, daily_CH4, CH4_surface, CH4_1.6m, CH4_3.8m, CH4_5m, CH4_9m,
         iCH4_surface, iCH4_1.6m, iCH4_3.8m, iCH4_5m, iCH4_9m)

# Select column pairs for comparison
selected_pairs <- list(
  c("CH4_surface", "iCH4_surface"),
  c("CH4_1.6m", "iCH4_1.6m"),
  c("CH4_3.8m", "iCH4_3.8m"),
  c("CH4_5m", "iCH4_5m"),
  c("CH4_9m", "iCH4_9m"),
  c("daily_CH4", "daily_CH4")
)

# Define colors for the two variables in each pair
colors <- c("blue", "red")

# Define a smaller legend size
legend_size <- 0.6

# Create a 2x3 plotting layout (will plot 5 pairs, leaving 1 empty)
par(mfrow = c(2, 3))  

# Loop through each selected pair and plot them
for (i in 1:length(selected_pairs)) {
  vars <- selected_pairs[[i]]
  
  # Plot first variable
  plot(gut_check$Date, gut_check[[vars[1]]], type = "p", col = colors[1], lwd = 2,
       xlab = "", ylab = "Value", main = paste("Pair", i, ":", vars[1], "vs", vars[2]))
  
  # Add second variable using lines()
  lines(gut_check$Date, gut_check[[vars[2]]], col = colors[2], lwd = 2)
  
  # Add a legend
  legend("topright", legend = vars, col = colors, pch = 1, lty = 1, lwd = 2, cex = legend_size, bg=rgb(1, 1, 1, 0.5))
}


```


#########################################################

### Structural Equation Modeling

#Resources:

#https://bookdown.org/luguben/EFA_in_R/determining-the-number-of-factors-1.html

#https://cran.r-project.org/web/packages/lavaanPlot/vignettes/Intro_to_lavaanPlot.html

#https://people.ucsc.edu/~zurbrigg/psy214b/09SEM8a.pdf

#Hu, L. T., & Bentler, P. M. (1999). Cutoff criteria for fit indexes in covariance structure analysis: Conventional criteria versus new alternatives. Structural equation modeling: a multidisciplinary journal, 6(1), 1-55.

#Sathyanarayana, S., & Mohanasundaram, T. (2024). Fit indices in structural equation modeling and confirmatory factor analysis: reporting guidelines. Asian Journal of Economics, Business and Accounting, 24(7), 561-577.


- First, we explored the relationships among various water quality variables and methane fluxes using a correlation plot. We did not include the independent variables strongly correlated with each other in the models to remove the effects of multicollinearity.


```{r}
#correlations
cor_data <- epi_hyp_int |> 
  select(-Date)

cor_matrix <- cor(cor_data, use="pairwise.complete.obs")
ggcorrplot(cor_matrix,
           lab = TRUE, lab_size = 2, tl.cex = 8)

```


The correlogram showed that the daily methane flux was most negatively correlated with dissolved oxygen saturation at 5m depth and 9m depth among the variables used. Also, daily methane flux was most positively correlated with volume-weighted dissolved methane concentration at 5m, thermocline depth and blue-green algae concentrations. #We then used short-listed variables from correlation analysis to define path analysis models and tested them against the weekly data. 

The model assumptions about univariate and multivariate normality was tested using shapiro-Wilk test and Mardia multivariate normality test.



```{r}
#Assessing assumptions about the distribution of measured variables
#Select only the columns we want to model
corr_data <- epi_hyp_int |> 
  select(daily_CH4, temp_surface, DOsat_5m, DOsat_9m, 
         sch_stab, Wind, iCH4_3.8m, thermo.depth, iCH4_1.6m, 
         iCH4_surface, iCH4_5m, iCH4_9m, temp_9m, temp_5m, 
         temp_4m, DOsat_1.6m, temp_1.6m, mean_Chla, mean_fDOM,
         DOsat_3.8m, DOsat_1.6m, daily_CH4)

#Test multivariate normality
mvnout <- mardia(corr_data)
mvnout$uv.shapiro #extract shapiro-Wilk univariate normality test statistics
mvnout$mv.test #Mardia multivariate normality test

```


- Results from both the univariate and multivariate tests indicate that the most measures do come from multivariate normal distributions.


```{r}
#NORMALIZE THE DATASET
data_scaled <- scale(corr_data)

```


### Individual path models and drivers selection

The piecewise SEM produces no valid global covariance matrix unlike latent variable based SEM, alternative goodness-of-fit tests are necessary. The typical approach uses Shipley's test of directed separation. This procedure tests the assumption that all variables are conditionally independent. In simplest terms, conditional independence implies that there are no missing relationships among unconnected variables (Shipley 2000a).

To compare standardized regression coefficients, we re-fit the model in lavaan package and assess the model fit using standardized test statistics (the ratio of chi-squared value to the degrees of freedom greater than 3), root mean squared error approximation (RMSEA) and standard root mean residual (SRMR) less than 0.1 and comparative fit index (CFI) grater than 0.9. 


The regression coefficients represent the strength of the relationship between latent constructs/ independent variables and dependent variable(s). Since, the latent constructs are correlated, the regression coefficients are partial coefficients, interpreted as the amount of change in dependent/ exogenous variable given a unit change in independent/ latent variable, controlling for the effects of other variables in the model.


```{r}
#select variables of interest
data_flux <- epi_hyp_int |> 
  select(DOsat_9m, temp_1.6m, temp_9m, temp_5m,
         iCH4_5m, iCH4_1.6m, DOsat_5m, 
         sch_stab, DOsat_1.6m, daily_CH4, 
         Wind, iCH4_9m, mean_Chla, mean_fDOM) |> 
  na.omit()
```


Diffusion model: In this concept, CH4 diffusion from hypolimnion to the epilimnion and subsequent flux to the atmosphere was modeled. 

```{r}
#diffusion model
#fit the path models
model_flux <- psem(
  lm(sch_stab ~  temp_1.6m + Wind, data_flux),
  lm(DOsat_1.6m ~  mean_Chla, data_flux),
  lm(iCH4_9m ~ DOsat_9m + sch_stab, data_flux),
  lm(iCH4_5m ~ DOsat_5m + iCH4_9m + mean_fDOM, data_flux),
  lm(iCH4_1.6m ~ Wind + DOsat_1.6m + mean_Chla + sch_stab + iCH4_5m, data_flux),
  lm(daily_CH4 ~ Wind + iCH4_1.6m + mean_Chla + temp_1.6m, data_flux)

)

summary(model_flux)


####MODEL TESTING IN LAVAAN PACKAGE######
#scale the dataset
data_flux_scaled <- scale(data_flux)

model_flux <- '
  sch_stab ~ temp_1.6m + Wind
  DOsat_1.6m ~  mean_Chla
  iCH4_9m ~ DOsat_9m + sch_stab
  iCH4_5m ~ DOsat_5m + iCH4_9m + mean_fDOM + sch_stab
  iCH4_1.6m ~ Wind + DOsat_1.6m + mean_Chla + sch_stab + iCH4_5m
  daily_CH4 ~ Wind + iCH4_1.6m + mean_Chla + temp_1.6m
  iCH4_5m ~~  iCH4_1.6m

'


fit.mod <- sem(model_flux, data = data_flux_scaled, std.lv = TRUE, estimator = "MLM")
#MODEL FIT (Ideally non-significant p-value OR the ratio of chisq.scaled:df.scaled less than 5)
fitMeasures(fit.mod, c("chisq.scaled", "df.scaled", "pvalue.scaled"))
#Check RMSEA to estimate the discrepancy between the model-based and observed correlation matrices which takes into account both chi-squared value and model parsimony.
#We want RMSEA <= 0.1
fitMeasures(fit.mod, c("rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "rmsea.pvalue.scaled"))
#Check CFI and SRMR
#We want CFI >= 0.9 and SRMR <= 0.08
fitMeasures(fit.mod, c("cfi.scaled", "srmr"))

#visualize the path diagrams
lavaanPlot(model = fit.mod, , graph_options = list(rankdir = "BT"), node_options=list(shape="box", fontname="Helvetica"), edge_options=list(color="grey"), coefs = TRUE, stand = TRUE, stars = c("regress", "latent"), digits=3, sig = TRUE)


```


Diffusion and Ebullition (5m) model: In this concept, an ebullition pathway from 5m depth was added to the diffusion model.


```{r}
#Ebullition from 5m with diffusion model
#fit the path models
model_flux <- psem(
  lm(sch_stab ~  temp_1.6m + Wind, data_flux),
  lm(DOsat_1.6m ~  mean_Chla, data_flux),
  lm(iCH4_9m ~ DOsat_9m + sch_stab, data_flux),
  lm(iCH4_5m ~ DOsat_5m + iCH4_9m + mean_fDOM, data_flux),
  lm(iCH4_1.6m ~ Wind + DOsat_1.6m + mean_Chla + sch_stab + iCH4_9m + iCH4_5m, data_flux),
  lm(daily_CH4 ~ Wind + iCH4_1.6m + iCH4_5m + mean_Chla + temp_1.6m, data_flux)

)

summary(model_flux)


####MODEL TESTING IN LAVAAN PACKAGE######
#scale the dataset
data_flux_scaled <- scale(data_flux)

model_flux <- '
  sch_stab ~ temp_1.6m + Wind
  DOsat_1.6m ~  mean_Chla
  iCH4_9m ~ DOsat_9m + sch_stab
  iCH4_5m ~ DOsat_5m + iCH4_9m + mean_fDOM + sch_stab
  iCH4_1.6m ~ Wind + DOsat_1.6m + mean_Chla + sch_stab + iCH4_9m + iCH4_5m
  daily_CH4 ~ Wind + iCH4_1.6m + iCH4_5m + mean_Chla + temp_1.6m
  iCH4_5m ~~  iCH4_1.6m

'


fit.mod <- sem(model_flux, data = data_flux_scaled, std.lv = TRUE, estimator = "MLM")
#MODEL FIT (Ideally non-significant p-value OR the ratio of chisq.scaled:df.scaled less than 5)
fitMeasures(fit.mod, c("chisq.scaled", "df.scaled", "pvalue.scaled"))
#Check RMSEA to estimate the discrepancy between the model-based and observed correlation matrices which takes into account both chi-squared value and model parsimony.
#We want RMSEA <= 0.1
fitMeasures(fit.mod, c("rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "rmsea.pvalue.scaled"))
#Check CFI and SRMR
#We want CFI >= 0.9 and SRMR <= 0.08
fitMeasures(fit.mod, c("cfi.scaled", "srmr"))

#visualize the path diagrams
lavaanPlot(model = fit.mod, , graph_options = list(rankdir = "BT"), node_options=list(shape="box", fontname="Helvetica"), edge_options=list(color="grey"), coefs = TRUE, stand = TRUE, stars = c("regress", "latent"), digits=3, sig = TRUE)

```


Diffusion and Ebullition (9m) model: In this concept, an ebullition pathway from 9m depth was added to the diffusion model.


```{r}
#Ebullition from 9m with diffusion model
#fit the path models
model_flux <- psem(
  lm(sch_stab ~  temp_1.6m + Wind, data_flux),
  lm(DOsat_1.6m ~  mean_Chla, data_flux),
  lm(iCH4_9m ~ DOsat_9m + sch_stab, data_flux),
  lm(iCH4_5m ~ DOsat_5m + iCH4_9m + mean_fDOM, data_flux),
  lm(iCH4_1.6m ~ Wind + DOsat_1.6m + mean_Chla + sch_stab + iCH4_9m + iCH4_5m, data_flux),
  lm(daily_CH4 ~ Wind + iCH4_1.6m + iCH4_9m + mean_Chla + temp_1.6m, data_flux)

)

summary(model_flux)


####MODEL TESTING IN LAVAAN PACKAGE######
#scale the dataset
data_flux_scaled <- scale(data_flux)

model_flux <- '
  sch_stab ~ temp_1.6m + Wind
  DOsat_1.6m ~  mean_Chla
  iCH4_9m ~ DOsat_9m + sch_stab
  iCH4_5m ~ DOsat_5m + iCH4_9m + mean_fDOM + sch_stab
  iCH4_1.6m ~ Wind + DOsat_1.6m + mean_Chla + sch_stab + iCH4_9m + iCH4_5m
  daily_CH4 ~ Wind + iCH4_1.6m + iCH4_9m + mean_Chla + temp_1.6m
  iCH4_5m ~~  iCH4_1.6m

'


fit.mod <- sem(model_flux, data = data_flux_scaled, std.lv = TRUE, estimator = "MLM")
#MODEL FIT (Ideally non-significant p-value OR the ratio of chisq.scaled:df.scaled less than 5)
fitMeasures(fit.mod, c("chisq.scaled", "df.scaled", "pvalue.scaled"))
#Check RMSEA to estimate the discrepancy between the model-based and observed correlation matrices which takes into account both chi-squared value and model parsimony.
#We want RMSEA <= 0.1
fitMeasures(fit.mod, c("rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "rmsea.pvalue.scaled"))
#Check CFI and SRMR
#We want CFI >= 0.9 and SRMR <= 0.08
fitMeasures(fit.mod, c("cfi.scaled", "srmr"))

#visualize the path diagrams
lavaanPlot(model = fit.mod, , graph_options = list(rankdir = "BT"), node_options=list(shape="box", fontname="Helvetica"), edge_options=list(color="grey"), coefs = TRUE, stand = TRUE, stars = c("regress", "latent"), digits=3, sig = TRUE)

```


Diffusion and Ebullition (5m and 9m) model: In this concept, an ebullition pathway from both 5m and 9m depth was added to the diffusion model.


```{r}
#Ebullition from 5m and 9m with diffusion model
#fit the path models
model_flux <- psem(
  lm(sch_stab ~  temp_1.6m + Wind, data_flux),
  lm(DOsat_1.6m ~  mean_Chla, data_flux),
  lm(iCH4_9m ~ DOsat_9m + sch_stab, data_flux),
  lm(iCH4_5m ~ DOsat_5m + iCH4_9m + mean_fDOM + sch_stab, data_flux),
  lm(iCH4_1.6m ~ Wind + mean_Chla + sch_stab + iCH4_9m + iCH4_5m + DOsat_1.6m, data_flux),
  lm(daily_CH4 ~ Wind + iCH4_1.6m + iCH4_9m + mean_Chla + temp_1.6m + iCH4_5m, data_flux)

)

summary(model_flux)


####MODEL TESTING IN LAVAAN PACKAGE######
#scale the dataset
data_flux_scaled <- scale(data_flux)

model_flux <- '
  sch_stab ~ temp_1.6m + Wind
  DOsat_1.6m ~ mean_Chla
  iCH4_9m ~ DOsat_9m + sch_stab
  iCH4_5m ~ DOsat_5m + iCH4_9m + mean_fDOM + sch_stab
  iCH4_1.6m ~ Wind +  sch_stab + iCH4_9m + iCH4_5m + DOsat_1.6m + mean_Chla
  daily_CH4 ~ Wind + iCH4_1.6m + iCH4_9m + mean_Chla + temp_1.6m + iCH4_5m
  iCH4_5m ~~  iCH4_1.6m

'


fit.mod <- sem(model_flux, data = data_flux_scaled, std.lv = TRUE, estimator = "MLM")
#MODEL FIT (Ideally non-significant p-value OR the ratio of chisq.scaled:df.scaled less than 5)
fitMeasures(fit.mod, c("chisq.scaled", "df.scaled", "pvalue.scaled"))
#Check RMSEA to estimate the discrepancy between the model-based and observed correlation matrices which takes into account both chi-squared value and model parsimony.
#We want RMSEA <= 0.1
fitMeasures(fit.mod, c("rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "rmsea.pvalue.scaled"))
#Check CFI and SRMR
#We want CFI >= 0.9 and SRMR <= 0.08
fitMeasures(fit.mod, c("cfi.scaled", "srmr"))

#visualize the path diagrams
lavaanPlot(model = fit.mod, graph_options = list(rankdir = "BT"), node_options=list(shape="box", fontname="Helvetica"), edge_options=list(color="grey"), coefs = TRUE, stand = TRUE, stars = c("regress", "latent"), digits=3, sig = TRUE)


```















